---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source("Analyzing Federal Reserve Annual Reports - A Text Analysis.R")
```

<body style="background-color:#E2F7F6;">
<center>
# FED Annual Reports: A Simple Text Analysis 
</center>

<br>
<br>
<hr>
<br>
<br>

### The aim of this project is to show the frequencies of the certain keywords in the annual reports of Federal Reserve between the years 1995 and 2018. The project identifies the most popular words year by year after excluding the unnecessary words that give no information on its own. Moreover, the project includes many visualisations.

<br>
<br>
<hr>
<br>
<br>


## I - Year by Year Inspection:{.tabset .tabset-fade}


<br>
<br>

### 1995{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_1995)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_1995,15)
```

<br>
<br>
<hr>
<br>
<br>
  
### 1996{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_1996)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_1996, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  
### 1997{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_1997)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_1997, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 1998{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_1998)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_1998, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 1999{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_1999)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_1999, 15)
```

<br>
<br>
<hr>
<br>
<br>
  

### 2000{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2000)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2000, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  
### 2001{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2001)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2001, 15)
```

<br>
<br>
<hr>
<br>
<br>
  

### 2002{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2002)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2002, 15)
```


<br>
<br>
<hr>
<br>
<br>
  
  
### 2003{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2003)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2003, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2004{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2004)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2004, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2005{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2005)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2005, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2006{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2006)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2006, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2007{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2007)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2007, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2008{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2008)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2008, 15)
```

<br>
<br>
<hr>
<br>
<br>
  

### 2009{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2009)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2009, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2010{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2010)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2010, 15)
```

<br>
<br>
<hr>
<br>
<br>
  

### 2011{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2011)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2011, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
### 2012{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2012)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2012, 15)
```

<br>
<br>
<hr>
<br>
<br>
  

### 2013{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2013)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2013, 15)
```

<br>
<br>
<hr>
<br>
<br>
  

### 2014{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2014)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2014, 15)
```
<br>
<br>
<hr>
<br>
<br>
  

### 2015{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2015)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2015, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2016{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2016)
```



<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>



```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2016, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  

### 2017{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2017)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2017, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  
### 2018{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
plot_popular_words(popular_2018)
```




<br>
<hr>
<center><h3>Most Popular 15 words: </h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "105%"}
head(popular_2018, 15)
```

<br>
<br>
<hr>
<br>
<br>
  
  
## II - Word Inspections:{.tabset .tabset-fade}


<br>
<br>

### Growth{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("growth")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "growth")
```

### Inflation{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("inflation")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "inflation")
```

### Unemployment{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("unemployment")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "unemployment")
```

### Regulation{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("regulation")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "regulation")
```

### Institutions{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("institutions")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "institutions")
```

### Production{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("production")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "production")
```

### Productivity{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("productivity")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "productivity")
```


### Crisis{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("crisis")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "crisis")
```


### Inequality{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("inequality")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "inequality")
```



### Population{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("population")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "population")
```



### Green{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("green")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "green")
```


### Transfer{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("transfer")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "transfer")
```


### Energy{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("energy")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "energy")
```

### Credit{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("credit")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "credit")
```

### Capital{.tabset .tabset-fade}

```{r, warning = FALSE, echo = FALSE, fig.height = 10, fig.width = 15}
graph_word("capital")
```


<br>
<hr>
<center><h3>In Detail:</h3></center>
<br>


```{r, warning = FALSE, echo = FALSE, out.width = "150%"}
find_word(Report_List, "capital")
```
